Scheduling and Vectorization for MPC

### 2022-04-13 overleaf/paper_SIMD.tex
Add to paper section 4.2 (MUX and Pseudo PHI)

\ana{Benjamin?}

Once the compiler converts the code to SSA,
it transforms $\phi$-nodes that correspond to if-statements into MUX nodes.
From the 3-address CFG conversion step,
$\phi$-nodes corresponding to if-statements will be in a basic block
with the ``merge condition'' property.
For example, if $X_3 = \phi(X_1,X_2)$ is in a block with merge condition $C$,
the compiler transforms it into $X_3 = \mathit{MUX}(C, X_1, X_2)$.
Next, the compiler runs the dead code elimination algorithm from Cytron's SSA paper.
Then, the control-flow graph is \emph{linearized} into MPC source,
which has loops but no if-statements.
\benjamin{TODO: Add more here}

\ana{I think we need to add more here. Conversion from SSA to MPC Source is not so trivial.}

A pseudo $\phi$-node $X_1 = \phi(X_0,X_2)$ in a loop header is evaluated during circuit generation. If it is the 0-th iteration, then the $\phi$-node evaluates to $X_0$, otherwise, it evaluates to $X_2$.

>>>>

Once the compiler converts the code to SSA,
it transforms $\phi$-nodes that correspond to if-statements into MUX nodes.
From the 3-address CFG conversion step,
$\phi$-nodes corresponding to if-statements will be in a basic block
with the ``merge condition'' property.
For example, if $X_3 = \phi(X_1,X_2)$ is in a block with merge condition $C$,
the compiler transforms it into $X_3 = \mathit{MUX}(C, X_1, X_2)$.
Next, the compiler runs the dead code elimination algorithm from Cytron's SSA paper.

Then, the control-flow graph is \emph{linearized} into MPC source,
which has loops but no if-statements.
This means that both branches of all if-statements are executed,
and the MUX nodes determine whether to use results from the then-block or from the else-block.
The compiler linearizes the control-flow graph with a variation of breadth-first search.
Blocks with the ``merge condition'' property are only considered
the second time they are visited,
since that will be after both branches of the if-statement are visited.
Each time the compiler visits a block,
it adds the block's statements to the MPC source.
If the block ends in a for-instruction,
the compiler recursively converts the body and code after the loop to MPC source
and adds the for-loop and code after the loop to the main MPC source.
If the block does not end in a for-instruction,
the compiler recursively converts all successor branches to MPC source and
appends these to the main MPC source.

Now, the remaining $\phi$-nodes in MPC source are \emph{pseudo} $\phi$-nodes.
A pseudo $\phi$-node $X_1 = \phi(X_0,X_2)$ in a loop header is evaluated during circuit generation. If it is the 0-th iteration, then the $\phi$-node evaluates to $X_0$, otherwise, it evaluates to $X_2$.
